%
%  =======================================================================
%  ····Y88b···d88P················888b·····d888·d8b·······················
%  ·····Y88b·d88P·················8888b···d8888·Y8P·······················
%  ······Y88o88P··················88888b·d88888···························
%  ·······Y888P··8888b···88888b···888Y88888P888·888·88888b·····d88b·······
%  ········888······"88b·888·"88b·888·Y888P·888·888·888·"88b·d88P"88b·····
%  ········888···d888888·888··888·888··Y8P··888·888·888··888·888··888·····
%  ········888··888··888·888··888·888···"···888·888·888··888·Y88b·888·····
%  ········888··"Y888888·888··888·888·······888·888·888··888··"Y88888·····
%  ·······························································888·····
%  ··························································Y8b·d88P·····
%  ···························································"Y88P"······
%  =======================================================================
% 
%  -----------------------------------------------------------------------
% Author       : 焱铭
% Date         : 2023-07-19 13:15:53 +0800
% LastEditTime : 2023-08-24 19:24:30 +0800
% Github       : https://github.com/YanMing-lxb/
% FilePath     : \GUET_Thesis_LaTeX\Chapters\Abstract.tex
% Description  : 
%  -----------------------------------------------------------------------
%

% !Mode:: "TeX:UTF-8"


\begin{ChineseAbstract}
    LaTeX利用设置好的模板，可以编译为格式统一的pdf。目前国内大多出版社与高校仍在使用word，word由于其强大的功能与灵活性，在新手面对形式固定的论文时，排版、编号、参考文献等简单事务反而会带来很多困难与麻烦，对于一些需要通篇修改的问题，要想达到LaTeX的效率，对word使用者来说需要具有较高的技能水平。

    为了能把主要精力放在论文撰写上，许多国际期刊和高校都支持LaTeX的撰写与提交，新手不需要关心格式问题，只需要按部就班的使用少数符号标签，即可得到符合要求的文档。且在需要全篇格式修改时，更换或修改模板文件，即可直接重新编译为新的样式文档，这对于word新手使用word的感受来说是不可思议的。
    此项目提供用于排版桂林电子科技大学本硕博(非全，在职)毕业论文(设计)LaTeX模板类，旨在帮助桂林电子科技大学的毕业生高效地完成毕业论文的写作。

\ChineseKeyword{桂林电子科技大学；本硕博学位论文；\LaTeX 模板类}
\end{ChineseAbstract}


\begin{EnglishAbstract}
    LaTeX can be compiled into a pdf of uniform format using the set template.At present, most domestic publishers and universities still use word. Because of its powerful function and flexibility, when faced with fixed-form papers by novices, simple matters such as typesetting, numbering, and reference documents will bring many difficulties and troubles. For some problems that need to be modified throughout, to achieve the efficiency of LaTeX, it requires a high level of skill for word users.

    In order to focus on the writing of papers, many international journals and universities support the writing and submission of LaTeX. Novices don't need to care about formatting issues. They only need to use a few symbolic labels step by step to get the documents that meet the requirements. And when you need to modify the entire format, you can directly recompile the template file by replacing or modifying the template file. This is incredible for the word novice to use the word.

    This project provides the LaTeX template class for typesetting the graduation thesis (design) of Guilin University of Electronic Science and Technology, aiming to help graduates of Guilin University of Electronic Science and Technology efficiently complete the writing of their graduation thesis.


\EnglishKeyword{GUET; Common template; \LaTeX;}
\end{EnglishAbstract}